\plaintitle

### 2017-01-08 drafts/labor/decomposition.tex
decomposition revision

\citeauthor{Brown01041990} inquired from another direction,
asking
what limited the adoption of piecework in industries that otherwise gravitated toward it
(in the case studies he examined,
this mostly focused on railway engineers),
ultimately arguing that factors such as the nature of the work design
(specifically,
the homogeneity of tasks) and the costs associated with adopting a piecework model
were the major contributing factors that determined the use of piecework~\cite{Brown01041990}.

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for the better part of a century.}
The beginnings of
systematic task decomposition 
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics,
including
`Arithmetic,
the use of Logarithms,
and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second, tasks were discrete
--- that is,
independent from one another.
Third, workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.

\topic{Piecework researchers enumerate a number of problems with the decomposition of work,
and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks,
because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
Ultimately, \citeauthor{bewley1999wages} argues that
``[piecework is] infeasible,
because~\dots~total output is the joint product of varying groups of people''~\cite{bewley1999wages}.

>>>>

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for the better part of a century.}
Decomposition was arguably the main innovation of Airy's human computers.
Rather than hire expert computers, Airy identified ways to break down astrological calculations into steps that could be completed with only a basic knowledge of mathematics.
Future piecework efforts followed a similar model.

\topic{Decomposability is core to piecework: one cannot pay by the piece unless the pieces are small and discretizable.}
Focusing on our case study of railway engineers, \citeauthor{Brown01041990} asked 
what enabled and limited the adoption of piecework.
He argued that the main determinants were task homogeneity and the fixed costs of the machinery and training~\cite{Brown01041990}.
In other words, if tasks could be clearly decomposed and defined, and if the firm could afford the training and machinery for the pieceworkers, piecework tended to be adopted.

Decomposition ultimately led to quantification and scientific management.
With \citeauthor{taylor1914principles}'s formalization of scientific management in \textit{Taylorism}
(and Henry Ford's eponymously named \textit{Fordism}),
piecework in the early and mid--\nth{20} century surged, especially in industrial work.
Scientific management promised that the careful measurement of workers would yield
higher efficiency and output~\cite{taylor1914principles,towardsGlobalFordism}.
While \citeauthor{Brown01041990} points out that
piecework dramatically advanced the instrumented measurement of workers,
in \citeauthor{taylor1914principles}'s time highly instrumented,
automatic measurement of workers was all but impossible~\cite{Brown01041990}.
Instead, managers conducted ``stop watch time studies''~\cite{nadworny1955scientific},
using completion times to inform per--task compensation,
similarly to the efficiency experts hired in the Santa Fe Railway, but
substantially more precise.
As a result, the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

\topic{Piecework researchers enumerate a number of problems with the decomposition of work,
and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks,
because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
%Ultimately, \citeauthor{bewley1999wages} argues that
%``[piecework is] infeasible,
%because~\dots~total output is the joint product of varying groups of people''~\cite{bewley1999wages}.
To \citeauthor{bewley1999wages}, the main limiter was the ability to define and measure the work.
